Software Ticket Quality

### 2017-10-14 proposal/mprop.tex
Added structure to the literature review subsection of the proposal

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey}

present an overview of relevant previous work including articles, books, and existing software products. Critically evaluate the strengths and weaknesses of the previous work.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey - I believe this is Lit Review?}

\subsection{Introduction}

\subsection{What was covered and why}

\subsection{How papers were found - what terms were searched for + snowballing}

\subsection{Data Quality Metrics}

\subsection{Issue Quality}

\subsection{Measuring Cost and Waste in Software Projects}

\subsection{Sentiment Analysis}

\subsection{Conclusion}
